---
title: 'R Course: Lesson 2'
author: "Page Piccinini"
date: "February 18, 2016"
output: pdf_document
---
```{r, echo=FALSE}
load("rcourse_lesson2_environment.RData")
```

# Introduction

I looked at how common my name, "Page", is in the United States population both by year and sex.


# Results

## Prevelence by Year

Below is a plot for how the proportion of people with the name "Page" (log-transformed) has changed over time. Over the trend is pretty flat, with maybe a slight increase over time.

```{r, fig.align='center'}
year.plot
```

To test if there is a significant effect of year a linear model was built. Proportion of the population log-transformed was the dependent variable and year the independent variable. As shown below, year was not significant, although the coefficients do show a positive slope.

```{r}
year.lm_sum
```

## Prevelence by Sex

Below is a plot for the proportion of people with the name "Page" (log-transformed) by sex. It appears there is a clear effect of sex, where it is a less popular name for males than females.

```{r, fig.align='center'}
sex.plot
```

To test if there is a significant effect of sex a linear model was built. Proportion of the population log-transformed was the dependent variable and sex the independent variable. As show below, sex was significant, with the name being less common in males than females [R^2^ = 0.15, F(1, 172) = 32.23, *p* < 0.001].

```{r}
sex.lm_sum
```